Correcting K-correction: fixing the time dilation and zero-point terms resolves the Hubble tension and removes evidence for accelerating expansion

### 2025-01-04 paper/dark_energy_corrections.tex

\title{Correcting K-correction: restoring the time dilation term and fixing the
inverted zero-point term removes accelerating expansion and resolves the Hubble
tension}

@@

\begin{abstract}
We rederive the K-correction equation and discover that the version of the
equation used in modern cosmology contains three errors. The oldest of these
errors traces back nine decades; in 1930 the equation did not correct for
spectral bandwidth stretching, followed by a rederivation in 1968 that
accounted for spectral bandwidth stretching but did not correct for time
dilation. Two new errors were introduced in 1996, one of which causes
systematic distance biases by inverting the zero-point correction term. We
conclude that properly correcting apparent magnitudes for redshift resolves two
of the preeminent mysteries in cosmology: first, dark energy is not supported
by observations of Type Ia supernovae and second, the Hubble tension is due to
the errors in the K-correction equation.
\end{abstract}

@@

Since the K-correction error has corrupted all astronomical measurements that
depend on both magnitude and redshift, a lot of data needs to be reanalysed.
Only once the data is cleaned can cosmological parameters, such as those used
by the Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the
$\Lambda$-CDM model, be reevaluated.

>>>>

\title{Correcting K-correction: fixing the time dilation and zero-point terms resolves the Hubble tension and removes evidence for accelerating expansion}

@@

\begin{abstract}
We rederive the K-correction equation and discover that the version of the
equation used to compute magnitudes contains three errors. The oldest of these
errors traces back nine decades; in 1930 the equation did not correct for
spectral bandwidth stretching, followed by a rederivation in 1968 that
accounted for spectral bandwidth stretching but did not correct for time
dilation. Two new errors were introduced in 1996, one of which causes
systematic distance biases by inverting the zero-point correction term. We
conclude that properly correcting apparent magnitudes for redshift resolves two
of the preeminent mysteries in cosmology: first, dark energy is not supported
by observations of Type Ia supernovae and second, the Hubble tension is due to
the errors in the K-correction equation.
\end{abstract}

@@

Since the K-correction error has corrupted all astronomical measurements that
depend on both magnitude and redshift, a lot of data needs to be reanalysed.
Cosmological parameters, such as those used by the
Friedmann-Lema\^{i}tre-Robertson-Walker (FLRW) metric or the $\Lambda$-CDM
model, can only be recalculated once the data is cleaned.
